%SecureComm 2017, up to 20 pages.
% June 21, 2017.

\documentclass[lnicst]{svmultln}
%
\usepackage{makeidx}  % allows for indexgeneration
% \makeindex          % be prepared for an author index
%
\usepackage{graphicx}
\usepackage{amssymb}


\begin{document}
%
\mainmatter              % start of the contribution
%
\title{A-Tor: Accountable Anonymity in Tor}
%
\titlerunning{A-Tor: Accountable Anonymity in Tor}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Quanwei Cai\inst{1,3} \and Jonathan Lutes\inst{2} \and Jingqiang Lin\inst{1,3,4} \and
  Bo Luo\inst{2}}
%
\authorrunning{Q. Cai, J. Lutes, J. Lin, and B. Luo}   % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Quanwei Cai, Jonathan Lutes, Jingqiang Lin, Bo Luo}
%
\institute{State Key Laboratory of Information Security, Institute of Information Engineering,\\Chinese Academy of Sciences, Beijing 100093, CHINA
\and
Department of Electrical Engineering and Computer Science,\\
the University of Kansas, KS 66045, USA
\and
Data Assurance and Communications Security Research Center,\\Chinese Academy of Sciences, Beijing 100093, CHINA
\and
University of Chinese Academy of Sciences, Beijing 100049, CHINA}

\maketitle              % typeset the title of the contribution
% \index{Ekeland, Ivar} % entries for the author index
% \index{Temam, Roger}  % of the whole volume
% \index{Dean, Jeffrey}

\begin{abstract}        % give a summary of your paper

% 匿名很重要，Tor用得很多。
% 但是，匿名有的时候被用来发起攻击等等，就使得Exit Node承担了法律责任。
% 本文扩展了Tor，提出了基于Tor的可撤销匿名方案。
% 基本原理是，利用Tor申请得到匿名证书（Cert Node）；再使用该匿名证书来发起匿名通信。
%（使用了不同于上一个的Tor Circuit；分别称为A-Tor circuit和Tor circuit）。
% Cert Node签发的证书应该被Exit Node所相信。
% 当Exit Node被追查攻击数据包时，执法方就可以沿着A-Tor circuit，一致追踪到用户。
% 分析表明，我们的方案具有的效果：与Tor具有相同的安全强度；直接使用现有的Tor的各种节点；不需要绝对可信的一方。
%


%Anonymity is needed for protecting privacy,
% and
 Tor is the most popular anonymous communication system in the Internet.
%  as it achieves a tradeoff between anonymity, usability and efficiency.
In Tor, each user chooses a sequence of onion routers (ORs) to construct a circuit to relay his/her network packets.
%and send messages through the circuit to the Internet to achieve anonymity.
%In Tor, clients choose a path through the network and build a circuit, the node in which is called onion router, to connect to the Internet anonymously.
%the end-node of the circuit
The final OR of the Tor circuit, called the exit node,
   forwards regular IP traffic for the Tor user to the destination server.
As a result, the exit nodes are often accused %liable
   of the anonymous users' illegal network activities.
% be placed a heavy burden, for example, some user uses Tor for illegal activities.
In this paper, we propose an extension for Tor, called \emph{A-Tor},
  to provide accountable anonymity.
A-Tor protects the exit nodes with verifiable proofs
  that the illegal or malicious packets are originated from the certain users but not the exit nodes.
An A-Tor user firstly constructs a Tor circuit to apply for an anonymous certificate.
Then,
 a second Tor circuit is constructed to access the destination server as in Tor,
  and the anonymous certificate is presented as a credential to the exit node;
 otherwise, the exit node refuses to forward his/her packets to the destination.
A-Tor provides anonymity with the same level of assurance as Tor,
  and cooperative ORs are able to trace the anonymous A-Tor user
     (when illegal or malicious packets are detected in the future).
Moreover,
  non-repudiation is achieved in the revocation of anonymity;
that is,
during the application of anonymous certificates and the subsequent anonymous communications through Tor circuits,
  a chain of evidences are generated by the A-Tor user and the ORs,
  and these evidences cannot be forged by collusive ORs.
%  , which makes them free of the consequence of the users' traffic,
%SafeExit introduces a circuit of audit onion routers %trusted entities
%  to generate such proofs, and to
%       find the initiator of (illegal) traffic when necessary.
%Our theoretical analysis shows that SafeExit does not degrade the anonymity of Tor,
%  moreover, it is expected to attract more nodes to serve as exit nodes, which in turn improves the anonymity of Tor.
The performance introduced by the A-Tor extension is also evaluated.
%The evaluation shows that,
%  this extension doesn't introduce significant performance overhead, compared with the original Tor.
%  nor introduce significant performance overhead. % in both the ordinary operating and some  even when some trusted entities are compromised.


\keywords {Anonymous Communication, Tor, Accountability, Revocable Anonymity}
\end{abstract}
%

\input{chap/introduction}
\input{chap/backgroundandrelatedwork}
\input{chap/Overview}
%    \input{chap/naiive}
\input{chap/SafeExit}
\input{chap/security}
\input{chap/conclusion}

\bibliographystyle{splncs}
\bibliography{bib/Reference}

\end{document}
